---
title: "2025-exeRcise-sheet-3"
author: "Necati Deniz Baykus"
date: "2025-06-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Übunsblatt 03

### Necati Deniz Baykuş

Matrikel-Nr.: 12764981

Studiengang: Informatik

## Aufgabe 1)

#### d)

PROS: Very hard to lose files, great for collaboration

CONS: Takes up file space, doesn't work in the background

## Aufgabe 2)

#### a)


#### b)


## Aufgabe 3)


#### a)

```{r message=FALSE, warning=FALSE}
pixar_films <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-03-11/pixar_films.csv')

public_response <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-03-11/public_response.csv')
```

```{r message=FALSE, warning=FALSE}
pixar_films_clean <- subset(pixar_films, !is.na(film) )

unique(pixar_films_clean$film_rating)

pixar_films_clean <- subset(pixar_films_clean,
                            film_rating %in% c("G", "PG"))


pixar_films_clean$film_rating <- factor(pixar_films_clean$film_rating,
                                        levels = c("G", "PG"),
                                        ordered = TRUE)

```

A factor is appropriate because film rating is a categorical subject. Assisgning a factor to it may help with further commands and analysis.

#### b)
```{r message=FALSE, warning=FALSE}

print(pixar_films_clean$film)

unique(pixar_films_clean$film)

pixar_films_clean$series <- NA

pixar_films_clean$series[grepl("Toy Story", pixar_films_clean$film)] <- "Toy Story"
pixar_films_clean$series[grepl("Cars", pixar_films_clean$film)] <- "Cars"
pixar_films_clean$series[grepl("Incredibles", pixar_films_clean$film)] <- "The Incredibles"
pixar_films_clean$series[grepl("Finding", pixar_films_clean$film)] <- "Finding"
pixar_films_clean$series[grepl("Monsters", pixar_films_clean$film)] <- "Monsters, Inc."


library(dplyr)

series_summary <- pixar_films_clean %>%
  filter(!is.na(series)) %>%
  group_by(series) %>%
  summarise(
    titles = paste(film, collapse = "; "),
    film_count = n()
  )

print(series_summary)

```

#### c)
```{r message=FALSE, warning=FALSE}
cinema_levels <- c( "A-", "A", "A+")

public_response$cinema_score <- factor(public_response$cinema_score,
                                       levels = cinema_levels,
                                       ordered = TRUE)

pixar_full <- merge(pixar_films_clean, public_response, by = "film", all.x= TRUE)

```

#### d)
```{r message=FALSE, warning=FALSE}

pixar_full$release_date <- as.Date(pixar_full$release_date)

library(dplyr)

series_films <- pixar_full %>%
  filter(!is.na(series)) %>%   
  arrange(series, release_date) %>%
  group_by(series) %>%
  mutate(title_ordered = factor(film, levels = unique(film)))

colnames(series_films)

head(pixar_full$rotten_tomatoes)

colnames(public_response)


library(ggplot2)
ggplot(series_films, aes(x = series, y = rotten_tomatoes, fill = title_ordered)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  labs(
    title = "Rotten Tomatoes Scores by Pixar Film Series",
    x = "Film Series",
    y = "Rotten Tomatoes Score",
    fill = "Film Title"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

A pattern is easily identifiable from the graph: The first films of the series have the best ratings or equally high ratings as the other highest rated film in the series.

